---
title: "Case study"
output: github_document
---
```{r setup, include = FALSE}
library(tidyverse)
library(p8105.datasets)
library(leaflet)


knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Load the airbnb data

```{r}
data("nyc_airbnb")
```




## Brainstorm some questions

* what is the best Airbnb in staten island for <$100
* what price range is popular in each borough?  most rented?
* what apartment features are related to price?
* cheapest room type in each neighborhood?
* hosts that have higher ratings?

## 


```{r}
nyc_airbnb =
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2)
```

```{r}
nyc_airbnb %>% 
  count(neighbourhood_group, room_type) %>% 
  pivot_wider(names_from = room_type, values_from = n)
```

```{r}
nyc_airbnb %>% 
  group_by(neighbourhood_group, room_type) %>% 
  summarize(mean_price = mean(price))
```

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = neighbourhood_group, y = price)) +
  geom_boxplot()
```

```{r}
nyc_airbnb %>% 
  filter(price < 1000) %>% 
  ggplot(aes(x = neighbourhood_group, y = price)) +
  geom_boxplot()
```

```{r}
nyc_airbnb %>% 
  filter(neighbourhood_group == "Manhattan") %>% 
  count(neighbourhood)

nyc_airbnb %>% 
  filter(
    price < 1000,
    neighbourhood_group == "Manhattan"
    ) %>% 
  mutate(
    neighbourhood = fct_reorder(neighbourhood, price)
  ) %>% 
  ggplot(aes(x = neighbourhood, y = price)) +
  geom_boxplot() +
  coord_flip()
```

```{r}
nyc_airbnb %>% 
  sample_n(1000) %>% 
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point()
```


## create a leaflet map

```{r}
nyc_airbnb %>% 
  sample_n(10) %>% 
  leaflet() %>% 
  addTiles() %>% 
  addMarkers(~lat, ~long)
```

```{r}
nyc_airbnb %>% 
  sample_n(100) %>% 
  leaflet() %>% 
  addTiles() %>% 
  addMarkers(~lat, ~long)
```

```{r}
nyc_airbnb %>% 
  sample_n(100) %>% 
  leaflet() %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addMarkers(~lat, ~long)
```

```{r}
pal <- colorNumeric("viridis", nyc_airbnb %>% pull(stars))

nyc_airbnb %>% 
  sample_n(5000) %>% 
  leaflet() %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addCircleMarkers(~lat, ~long, , radius = 1, color =~ pal(stars))
```

```{r}
pal <- colorNumeric("magma", nyc_airbnb %>% pull(stars))

nyc_airbnb %>% 
  drop_na(stars) %>% 
  sample_n(5000) %>% 
  leaflet() %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addCircleMarkers(~lat, ~long, , radius = 1, color =~ pal(stars))
```


* thought process.  wanted to look at a plot of rentals in the area - made a plot in ggplot using lat and long for x and y.  then, he had heard in the past the leaflet package and googled it and learned about it, tried to copy and paste code from an online source to see what it does.  Same infrastructure and foundation - to build later on other things (e.g., leaflet package), cut and paste code from online, and make some adjustments.  the key is started off with some question.  created a map to see where things exist - and interact with these things - see properties of airbnb rentals in relation to their location.

* leaflet works like ggplot, as well as other package we will see in later weeks.  (plotly).  same kind of idea, same design principle.  that's why it is helpful to learn ggplot and hope it operates.

* all the stuff prior to leaflet - filtering, grouping, summarizing, pivoting were all techniques we used.  the factor relevel is a new-ish concept/code.  also the leaflet stuff.  practice the tools you need to work with data.